Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-06-11 LaTeX_paper/paper.tex
add new images

>>>>

  \item \textbf{Find the coordinates of the four corners}\newline
  To find the coordinates of the corners, the program uses a tree steps approximation.
  It initially finds the minimum enclosing rectangle,
  and uses the coordinates of the corners of the rectangle
  as first approximation.\newline
  As a second approximation it takes
  the white pixel that is closest to the first approximation.
  Then it considers only the pixels that are within a certain
  distance of the second approximation, and finds the minimum
  enclosing triangle of sed pixels.\newline
  The corner of the triangle that is closest to the second
  approximation is the third and final approximation
  of the corner of the piece.

  \item \textbf{Split each side using the previously found coordinates.}\newline
	Once the program has found the four coordinates of the corners, to obtain each
  side,it just needs to rotate and crop the piece, and so obtain a single side.
\end{itemize}
